Title: "Peer Assignment 1 Repoducible Research"
Author: "Deepali Gupta"
Date: "Tuesday, July 14, 2015"
Output: html_document

Dataset : Activity Monitoring Data

Reading th dataset and filtering all the rows not containing NA
Total no of Steps taken per day

```{r}
library(dplyr)
activitydata <- read.csv("./activity.csv")
activityfilter <- filter(activitydata, !is.na(activitydata$steps))
groupactivitybydate <- group_by(activityfilter, date)
stepsperday <- summarize(groupactivitybydate, sum(steps))
head(stepsperday)
names(stepsperday) <- c("Date", "Steps")
```

Histogram of total number of steps taken per Day:

```{r, echo=TRUE}
table(stepsperday$Steps)
hist(stepsperday$Steps,xlab = "Steps", ylab = "Count", main = "No. of steps taken per day", col = "green")
```

Mean and Median of total number of steps taken per day

```{r}
mean(stepsperday$Steps, na.rm = TRUE)
median(stepsperday$Steps, na.rm = TRUE)
```


Time Series Plot of Average number of steps taken

```{r}
groupactivitybyinterval <- group_by(activityfilter, interval)
averagestepsbyinterval <- summarize(groupactivitybyinterval, sum(steps)/n())
names(averagestepsbyinterval) <- c("interval", "Average_Steps")
head(averagestepsbyinterval)
 with(averagestepsbyinterval, plot(interval, Average_Steps, type = "l", xlab = "Interval", ylab = "Average Steps", main = "Average number of Steps taken in 5-min interval", col = "blue"))
filter(averagestepsbyinterval, Average_Steps == max(averagestepsbyinterval$Average_Steps))
```

Imputing Missing Values

```{r}
##Total number of missing values in a dataset
sum(is.na(activitydata$steps))
##Strategy for filling all the missing values by mean of 5-min interval
meanstepsbyinterval <- summarize(groupactivitybyinterval, mean(steps))
names(meanstepsbyinterval) <- c("interval", "Mean_Steps")
fillNA <- numeric()
for(i in 1:nrow(activitydata))
  {
    obs <- activitydata[i, ]
    if(is.na(obs$steps))
      {
      steps <- subset(meanstepsbyinterval, interval == obs$interval)$Mean_Steps
      }
    else
      {
      steps <- obs$steps
    }
    fillNA[i] <- steps
  }
activitydatafillNA <- activitydata
activitydatafillNA$steps <- fillNA
head(activitydatafillNA)
##Histogram of total number of steps taken each day with mean and median
activitydatafillNAperday <- aggregate(steps ~ date, data = activitydatafillNA, FUN = sum)
hist(activitydatafillNAperday$steps, xlab = "Steps per Day", ylab = "Count", main = "Total No of Steps taken per day", col = "red")
mean(activitydatafillNAperday$steps)
median(activitydatafillNAperday$steps)
```
The estimate for the mean remain the same, However the estimate for median shifted a bit. For the days there was missing data has been replaced by mean of 5-min interval and the total no. of steps for each missing day is 10766.18.It increased th interval size of 10000-15000 by 8, since there were 8 missing days
